af2

### 2021-07-14 af2.Rmd
df

 ---
title: "additional3D"
output: pdf_document
---

@@

@@

df <- read.csv("df_tot.csv",sep =",")

# 
# 
# 
# 
# df_3D <- read.csv("3D.csv",sep=",")
# excl3D <- names(df_3D) %in% c("run", "density","step")
# df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
# 
# 
# value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
# excl <- names(value_basic_den) %in% c("run","density","step")
# value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)
# 
# 
# value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
# excl <- names(value_dominant_den) %in% c("run","density","step")
# value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean) 
#

>>>>

 ---
title: "af2"
output: pdf_document
---

@@

#setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/analysis")

@@

df <- read.csv("df_tot.csv",sep =",") %>% select(-c(run)) %>%
  group_by(ID,density,majority,liberal_maj,liberal_min,beta_distribution,con_maj,con_min,lib_maj,lib_min,dominant,secondary,con_eth,lib_val,lib_eth,con_val,eth_con_maj,eth_con_min,eth_lib_maj,eth_lib_min,val_con_maj,val_con_min,val_lib_maj,val_lib_min,step) %>% 
  summarise_all(c("m"= mean,"sd"= sd)) %>%  
  gather(key = group_bsl, value = Segra_bsl, et_cl_m,et_sq_m,vl_cl_m,vl_sq_m,den_cl_m,den_sq_m,
         et_cl_sd,et_sq_sd,vl_cl_sd,vl_sq_sd,den_cl_sd,den_sq_sd
         )  %>%
  mutate(`outcome` = fct_relevel(fct_collapse(group_bsl,"Ethnic" = c("et_sq_m","et_cl_m","et_sq_sd","et_cl_sd"), "Value" = c("vl_sq_m","vl_cl_m","vl_sq_sd","vl_cl_sd"), "Density" = c("den_sq_m","den_cl_m","den_sq_sd","den_cl_sd")),"Ethnic"),
`orientation` = fct_relevel(fct_collapse(group_bsl,"Conservatives" = c("et_sq_m","vl_sq_m","den_sq_m","et_sq_sd","vl_sq_sd","den_sq_sd"
                                                                       ), "Liberals" = c("et_cl_m","vl_cl_m","den_cl_m", "et_cl_sd","vl_cl_sd","den_cl_sd")), "Conservatives"),
`Stat` = fct_relevel(fct_collapse(group_bsl,"Mean" = c("et_cl_m","et_sq_m","vl_cl_m","vl_sq_m","den_cl_m","den_sq_m"), "SD" = c("et_cl_sd","et_sq_sd","vl_cl_sd","vl_sq_sd","den_cl_sd","den_sq_sd")),  "Mean")) %>%
  gather(key = group_asm, value = Segra_asm, cls_et_sq_bl_m,cls_et_cl_bl_m,cls_et_sq_or_m,cls_et_cl_or_m,
         cls_vl_sq_bl_m,cls_vl_cl_bl_m,cls_vl_sq_or_m,cls_vl_cl_or_m,
         cls_den_sq_bl_m,cls_den_cl_bl_m,cls_den_sq_or_m,cls_den_cl_or_m,
           et_sq_bl_m, et_cl_bl_m, et_sq_or_m, et_cl_or_m,
           vl_sq_bl_m, vl_cl_bl_m, vl_sq_or_m, vl_cl_or_m,
           den_sq_bl_m, den_cl_bl_m, den_sq_or_m, den_cl_or_m,

         cls_et_sq_bl_sd,cls_et_cl_bl_sd,cls_et_sq_or_sd,cls_et_cl_or_sd,
         cls_vl_sq_bl_sd,cls_vl_cl_bl_sd,cls_vl_sq_or_sd,cls_vl_cl_or_sd,
         cls_den_sq_bl_sd,cls_den_cl_bl_sd,cls_den_sq_or_sd,cls_den_cl_or_sd,
           et_sq_bl_sd, et_cl_bl_sd, et_sq_or_sd, et_cl_or_sd,
           vl_sq_bl_sd, vl_cl_bl_sd, vl_sq_or_sd, vl_cl_or_sd,
           den_sq_bl_sd, den_cl_bl_sd, den_sq_or_sd, den_cl_or_sd

         )%>% 
  mutate(`outcome` = fct_relevel(fct_collapse(group_asm, 
          "Ethnic" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m","et_sq_bl_m","et_cl_bl_m","et_sq_or_m","et_cl_or_m",
                       "cls_et_sq_bl_sd","cls_et_cl_bl_sd","cls_et_sq_or_sd","cls_et_cl_or_sd","et_sq_bl_sd","et_cl_bl_sd","et_sq_or_sd","et_cl_or_sd"

                       ),
           "Value" = c( "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m" ,"vl_sq_bl_m","vl_cl_bl_m","vl_sq_or_m","vl_cl_or_m",
                        "cls_vl_sq_bl_sd","cls_vl_cl_bl_sd","cls_vl_sq_or_sd","cls_vl_cl_or_sd" ,"vl_sq_bl_sd","vl_cl_bl_sd","vl_sq_or_sd","vl_cl_or_sd"
                        ),
           "Density" = c("cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m","den_sq_bl_m","den_cl_bl_m","den_sq_or_m","den_cl_or_m",
                         "cls_den_sq_bl_sd","cls_den_cl_bl_sd","cls_den_sq_or_sd","cls_den_cl_or_sd","den_sq_bl_sd","den_cl_bl_sd","den_sq_or_sd","den_cl_or_sd"
                         )
                                              ), "Ethnic"),

         `type` = fct_relevel(fct_collapse(group_asm,
            "Conservative Majority" = c("cls_et_sq_bl_m","cls_vl_sq_bl_m","cls_den_sq_bl_m", "et_sq_bl_m","vl_sq_bl_m","den_sq_bl_m",
                          "cls_et_sq_bl_sd","cls_vl_sq_bl_sd","cls_den_sq_bl_sd", "et_sq_bl_sd","vl_sq_bl_sd","den_sq_bl_sd"              
                                        ),
            "Liberal Majority" = c("cls_et_cl_bl_m","cls_vl_cl_bl_m","cls_den_cl_bl_m",  "et_cl_bl_m","vl_cl_bl_m","den_cl_bl_m",
                                   "cls_et_cl_bl_sd","cls_vl_cl_bl_sd","cls_den_cl_bl_sd",  "et_cl_bl_sd","vl_cl_bl_sd","den_cl_bl_sd"

                                   ),
             "Conservative Minority" = c("cls_et_sq_or_m","cls_vl_sq_or_m","cls_den_sq_or_m",  "et_sq_or_m","vl_sq_or_m","den_sq_or_m",
                                         "cls_et_sq_or_sd","cls_vl_sq_or_sd","cls_den_sq_or_sd",  "et_sq_or_sd","vl_sq_or_sd","den_sq_or_sd"

                                         ),
             "Liberal Minority" = c("cls_et_cl_or_m","cls_vl_cl_or_m","cls_den_cl_or_m", "et_cl_or_m","vl_cl_or_m","den_cl_or_m",
                                    "cls_et_cl_or_sd","cls_vl_cl_or_sd","cls_den_cl_or_sd", "et_cl_or_sd","vl_cl_or_sd","den_cl_or_sd"
                                    )
            ),"Conservative Majority" ),
         `metric` = fct_relevel(fct_collapse(group_asm,
            "Exposure" = c("et_sq_bl_m", "et_cl_bl_m", "et_sq_or_m", "et_cl_or_m", "vl_sq_bl_m", "vl_cl_bl_m", "vl_sq_or_m", "vl_cl_or_m", "den_sq_bl_m", "den_cl_bl_m",  "den_sq_or_m", "den_cl_or_m",
                           "et_sq_bl_sd", "et_cl_bl_sd", "et_sq_or_sd", "et_cl_or_sd", "vl_sq_bl_sd", "vl_cl_bl_sd", "vl_sq_or_sd", "vl_cl_or_sd", "den_sq_bl_sd", "den_cl_bl_sd",  "den_sq_or_sd", "den_cl_or_sd"
                           ),
            "Cluster" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m", "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m", "cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m",

      "cls_et_sq_bl_sd","cls_et_cl_bl_sd","cls_et_sq_or_sd","cls_et_cl_or_sd", "cls_vl_sq_bl_sd","cls_vl_cl_bl_sd","cls_vl_sq_or_sd","cls_vl_cl_or_sd", "cls_den_sq_bl_sd","cls_den_cl_bl_sd","cls_den_sq_or_sd","cls_den_cl_or_sd"

                          )), "Exposure"),
      `Stat` = fct_relevel(fct_collapse(group_asm,
                                        "Mean" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m",
         "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m",
         "cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m",
           "et_sq_bl_m", "et_cl_bl_m", "et_sq_or_m", "et_cl_or_m",
           "vl_sq_bl_m", "vl_cl_bl_m", "vl_sq_or_m", "vl_cl_or_m",
           "den_sq_bl_m", "den_cl_bl_m", "den_sq_or_m", "den_cl_or_m"),
         "SD" = c("cls_et_sq_bl_sd","cls_et_cl_bl_sd","cls_et_sq_or_sd","cls_et_cl_or_sd",
         "cls_vl_sq_bl_sd","cls_vl_cl_bl_sd","cls_vl_sq_or_sd","cls_vl_cl_or_sd",
         "cls_den_sq_bl_sd","cls_den_cl_bl_sd","cls_den_sq_or_sd","cls_den_cl_or_sd",
           "et_sq_bl_sd", "et_cl_bl_sd", "et_sq_or_sd", "et_cl_or_sd",
           "vl_sq_bl_sd", "vl_cl_bl_sd", "vl_sq_or_sd", "vl_cl_or_sd",
           "den_sq_bl_sd", "den_cl_bl_sd", "den_sq_or_sd", "den_cl_or_sd" )), "Mean"))

# df <- read.csv("df_tot.csv",sep =",") %>% select(-c(run)) %>%
#   group_by(ID,density,majority,liberal_maj,liberal_min,beta_distribution,con_maj,con_min,lib_maj,lib_min,dominant,secondary,con_eth,lib_val,lib_eth,con_val,eth_con_maj,eth_con_min,eth_lib_maj,eth_lib_min,val_con_maj,val_con_min,val_lib_maj,val_lib_min,step) %>% summarise_all(c("m"= mean,"sd"= sd)) %>%  gather(key = group_bsl, value = Segra_bsl, et_cl_m,et_sq_m,vl_cl_m,vl_sq_m,den_cl_m,den_sq_m)  %>%
#   mutate(`outcome` = fct_relevel(fct_collapse(group_bsl,"Ethnic" = c("et_sq_m","et_cl_m"), "Value" = c("vl_sq_m","vl_cl_m"), "Density" = c("den_sq_m","den_cl_m")),"Ethnic"),
# `orientation` = fct_relevel(fct_collapse(group_bsl,"Conservatives" = c("et_sq_m","vl_sq_m","den_sq_m"), "Liberals" = c("et_cl_m","vl_cl_m","den_cl_m")), "Conservatives") ) %>%
#   gather(key = group_asm, value = Segra_asm, cls_et_sq_bl_m,cls_et_cl_bl_m,cls_et_sq_or_m,cls_et_cl_or_m,
#          cls_vl_sq_bl_m,cls_vl_cl_bl_m,cls_vl_sq_or_m,cls_vl_cl_or_m,
#          cls_den_sq_bl_m,cls_den_cl_bl_m,cls_den_sq_or_m,cls_den_cl_or_m)%>% 
#   mutate(`outcome` = fct_relevel(fct_collapse(group_asm, "Ethnic" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m"),
#                                               "Value" = c( "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m"),
#                                               "Density" = c("cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m")
#                                               ), "Ethnic"),
#          `outcome` = fct_relevel(fct_collapse(group_asm, "Conservative Majority" = c("cls_et_sq_bl_m","cls_vl_sq_bl_m","cls_den_sq_bl_m"),
#                                               "Liberal Majority" = c("cls_et_cl_bl_m","cls_vl_cl_bl_m","cls_den_cl_bl_m"),
#                                               "Conservative Minority" = c("cls_et_sq_or_m","cls_vl_sq_or_m","cls_den_sq_or_m"),
#                                               "Liberal Minority" = c("cls_et_cl_or_m","cls_vl_cl_or_m","cls_den_cl_or_m")
#             )))
